Manuscript 1 code

### 2024-09-12 manuscript_1_code.Rmd
added synchrony cover model and plot

## figure 4c model - richness synchrony

```{r richness synchrony mod}
synch_stab_mod <- glmmTMB(cover_stability ~ synchrony*habitat + (1|site), family = Gamma("log"), data = diversity_stability_synchrony)
summary(synch_stab_mod)
hist(residuals(synch_stab_mod)) # looks good
plot(residuals(synch_stab_mod) ~ fitted(synch_stab_mod)) # same issue as always
r.squaredGLMM(synch_stab_mod) # 0.63, 0.71
emtrends(synch_stab_mod, pairwise ~ habitat, var = "synchrony") # fringing and backreef not different
```

@@

>>>>

## figure 4a no habitat

```{r richness stability no hab}
rich_stab_mod_2 <- glmmTMB(cover_stability~ richness_mean + (1|site), family = Gamma(link = "log"), data = diversity_stability_synchrony)
summary(rich_stab_mod_2)
hist(residuals(rich_stab_mod_2)) # a chunkier version
plot(residuals(rich_stab_mod_2) ~ fitted(rich_stab_mod_2)) # heteroskedastic - bring to group
r.squaredGLMM(rich_stab_mod_2) # 0.750, 0.757

```{r 4a no hab setup}
rich_stab_emm_2 <-as.data.frame(emmeans(rich_stab_mod_2, ~richness_mean,
                                     at = list(richness_mean = seq(min(diversity_stability_synchrony$richness_mean),
                                                            max(diversity_stability_synchrony$richness_mean),
                                                            0.01))))

## figure 4a no habitat plot

```{r figure 4a no habitat}
(figure_4a_no_hab <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = richness_mean, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects, aes(x = richness_mean, y = exp(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_rich_stab_effects, aes(x = richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  geom_line(data = rich_stab_emm_2, aes(x = richness_mean, y = exp(emmean)), size = 2, colour = "black") +
  geom_ribbon(data = rich_stab_emm_2, aes(x = richness_mean, ymin = exp(asymp.LCL), ymax = exp(asymp.UCL)), fill = "black",
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "Macroalgal Richness") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

ggsave(filename = "output/figure_4a_with_no_hab.png", figure_4a_no_hab, height = 10, width = 14)
```

## figure 4c model -  synchrony staability

```{r synchrony staability mod}
synch_stab_mod <- glmmTMB(cover_stability ~ synchrony*habitat + (1|site), family = Gamma("log"), data = diversity_stability_synchrony)
summary(synch_stab_mod)
hist(residuals(synch_stab_mod)) # looks good
plot(residuals(synch_stab_mod) ~ fitted(synch_stab_mod)) # same issue as always
r.squaredGLMM(synch_stab_mod) # 0.63, 0.71
emtrends(synch_stab_mod, pairwise ~ habitat, var = "synchrony") # fringing and backreef not different
```

@@

# Synchrony and cover

## synchrony and cover model

```{r synchrony cover mod}
synch_cov_mod <- glmmTMB(cover_mean ~ synchrony*habitat + (1|site), family = beta_family(), data = diversity_stability_synchrony)
summary(synch_cov_mod)

emtrends(synch_cov_mod, pairwise ~ habitat, var = "synchrony") # forereef 17 distinct from all other habitats
```

```{r synch cov mod setup}
synch_cov_emm <- emmip(synch_cov_mod,
                        habitat ~ synchrony,
                        at = list(synchrony = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synch_cov_effects <- synch_cov_emm %>%
  left_join(dss_ranges, by = c("habitat")) %>%
  filter(synchrony >= min_synchrony & synchrony <= max_synchrony)
```

```{r synchrony cover plot}
(synchrony_cover_plot <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_cov_effects, aes(x = synchrony, y = exp(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_synch_cov_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "Synchrony", y = "Cover\n") +
  theme_bw() + 
  theme(axis.title.x = element_text(size=18), 
        axis.title.y = element_text(size=18), 
        panel.background = element_blank(), 
        panel.grid.major = element_blank(),  #remove major-grid labels
        panel.grid.minor = element_blank(),  #remove minor-grid labels
        plot.background = element_blank(),
        legend.text = element_text(size = rel(1)), # increase legend text
        legend.title = element_text(size = rel(1)),
        legend.position = 'bottom', # move legend to bottom
        legend.box = 'horizontal', # make legend horizontal
        legend.box.background = element_rect(colour = "black"))  # add box around legend
         )

ggsave(filename = "output/synchrony_cover_plot.png", synchrony_cover_plot, height = 10, width = 14)
```
